Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
write on VI.B about boundary artifacts

\subsection{Invariance and stability in acoustic scenes}
The notion of invariance to time shifts plays an essential role in acoustic scene similarity retrieval as well as acoustic scene classification.
Indeed, recordings may be shifted locally without affecting their perception and therefore such shifts do not convey any information about the class.
To discard this superfluous source of variability, signals can be mapped to a time-shift invariant feature space before training the classifier, eliminating the need for the classifier to explicitly learn this invariance.
From any set of descriptors $\boldsymbol{x_1}(t,\gamma)$, where $\gamma$ denotes a descriptor index, a representation invariant to time shifts shorter in duration than $T$ can be obtained by convolving $\boldsymbol{x_1}$ with a low-pass filter $\boldsymbol{\phi}(t)$ of cutoff frequency set to $1/T$, as measured in Hertz:
\begin{equation}
\mathbf{S_1}\boldsymbol{x}(t, \gamma) = (\boldsymbol{x_1} \ast \boldsymbol{\phi}) (t).
\end{equation}
A downside is that the transient information in $\boldsymbol{x_1}$ at scales finer than $T$ are lost by this low-pass filtering, reducing discriminability in feature space.
To address this issue, the temporal scattering transform recovers this information by convolving $\boldsymbol{x_1}$ with wavelets whose center frequencies are above $1/T$ and then applying complex modulus.

@@

The next subsection describes the operations involved in temporal scattering, and in particular the construction of wavelet filter banks.

@@

A drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene.
In the context of the DCASE 2013 dataset, this corresponds to merely $8$ training instances per class, and $80$ instances overall, hence an increase in variance in statistical estimation and a risk of overfitting. \ja{That may be, but by averaging, we also reduce the variability of our data, which may be a good thing. If we're dealing with Gaussian processes, this is in fact a very good thing to do.}
On the contrary, a late integration scheme for $T=372\textrm{ ms}$ would yield $128$ instances per auditory scene \ja{How long is each recording? Should we specify this somewhere?}, resulting in $10240$ instances overall.
However, many of these instances may be silent or lack any salient properties of the class they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition. \ja{Another important difference is that early integration makes the classifier objective more appropriate, since the SVM will maximize the final classification error on the training data, as opposed to some intermediate frame-level label.}
In the context of this paper, early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions. 
%\ja{We should perhaps mention this in that particular section instead of over here.}
\subsection{Standardization}
\label{sec:stand}

@@

Experiments are carried out using temporal scattering coefficients as well as mel-frequency cepstral coefficients (MFCCs) as features. For the temporal scattering, each scene is described by $128$ vectors of scattering coefficients computed with half-overlapping windows $\boldsymbol{\phi}(t)$ of duration $T=372\,\mathrm{ms}$. Experiments are conducted with and without the logarithmic compression (see Section \ref{sec:logcomp}).

>>>>

\subsection{Invariance and stability in acoustic scenes}
The notion of invariance to time shifts plays an essential role in acoustic scene similarity retrieval as well as acoustic scene classification.
Indeed, recordings may be shifted locally without affecting their perception and therefore such shifts do not convey any information about the class.
To discard this superfluous source of variability, signals can be mapped to a time-shift invariant feature space before training the classifier, eliminating the need for the classifier to explicitly learn this invariance.
From any set of descriptors $\boldsymbol{x_1}(t,\gamma)$, where $\gamma$ denotes a descriptor index, a representation invariant to time shifts shorter in duration than $T$ can be obtained by convolving $\boldsymbol{x_1}$ with a low-pass filter $\boldsymbol{\phi}(t)$ of cutoff frequency set to $1/T$, as measured in Hertz:
\begin{equation}
\mathbf{S_1}\boldsymbol{x}(t, \gamma) = (\boldsymbol{x_1} \ast \boldsymbol{\phi}) (t).
\end{equation}
A downside is that the transient information in $\boldsymbol{x_1}$ at scales finer than $T$ are lost by this low-pass filtering, reducing discriminability in feature space.
To address this issue, the scattering transform recovers this information by convolving $\boldsymbol{x_1}$ with wavelets whose center frequencies are above $1/T$ and then applying complex modulus.

@@

The next subsection describes the operations involved in the scattering transform, and in particular the construction of wavelet filter banks.

@@

A drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene.
In the context of the DCASE 2013 private dataset, this corresponds to merely $8$ training instances per class, and $80$ instances overall, hence an increase in variance in statistical estimation and a risk of overfitting. \ja{That may be, but by averaging, we also reduce the variability of our data, which may be a good thing. If we're dealing with Gaussian processes, this is in fact a very good thing to do.}
On the contrary, a late integration scheme for $T=372\textrm{ ms}$ would yield $128$ instances per auditory scene \ja{How long is each recording? Should we specify this somewhere?}, resulting in $10240$ instances overall.
However, many of these instances may be silent or lack any salient properties of the class they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition. \ja{Another important difference is that early integration makes the classifier objective more appropriate, since the SVM will maximize the final classification error on the training data, as opposed to some intermediate frame-level label.}
In the context of this paper, early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions. 
%\ja{We should perhaps mention this in that particular section instead of over here.}
\subsection{Standardization}
\label{sec:stand}

@@

Experiments are carried out using scattering coefficients as well as mel-frequency cepstral coefficients (MFCCs) as features. For the scattering transform, each $30$-second scene is described by $128$ vectors computed with half-overlapping windows $\boldsymbol{\phi}(t)$ of duration $T=372\,\mathrm{ms}$, for a total of $24\,\mathrm{s}$. Indeed, $3$ seconds are discarded at the beginning and at the end of the scene so as to avoid boundary artifacts.  Experiments are conducted with and without the logarithmic compression (see Section \ref{sec:logcomp}).
